---
output:
  html_document: default
  pdf_document: default
---
## R Markdown
---
<font size="3">
---
title: "MGT_6203_HW3_Part2_kbiswas7"
author: "kbiswas7"
date: "4/11/2020"
output: pdf_document
---
</font/>
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_package}
#Download required packages
if (!require(DataExplorer)) install.packages("DataExplorer")
library(DataExplorer)
if (!require(dplyr)) install.packages("dplyr")
library(dplyr)
if (!require(ggplot2)) install.packages("ggplot2")
library(ggplot2)
```

## R Markdown
<font size="3">Instructions for Q.1 to 4
Please use the Facebook Ad dataset KAG_data.csv (https://www.dropbox.com/s/z0nh7udu19cn494/KAG__data.csv) for the next set of
questions. We advise solving these questions using R (preferably using dplyr library wherever applicable) after reviewing the code
provided for Week 11 and other resources provided for learning dplyr in R Learning Guide.
Load the dataset as below:
</font/>
```{r dataload}
data <- read.csv("KAG.csv", stringsAsFactors = FALSE)
```

## R Markdown
Exploring the data
```{r}
glimpse(data)
```

## R Markdown
<font size="3">Q.1 Which ad (provide ad_id as the answer) among the ads that have the least CPC led to the most impressions?</font/>
```{r Q1}
min_cpc <- min(data$CPC)
data %>% filter(CPC == min(CPC)) %>% filter(Impressions == max(Impressions)) %>% select(ad_id)
```

## R Markdown
<font size="3">Q.2 What campaign (provide compaign_id as the answer) had spent least efficiently on brand awareness on an average(i.e. most Cost per
mille or CPM: use total cost for the campaign / total impressions in thousands)?</font/>
```{r Q2}
data <- data %>% mutate(CPM = round((Spent / Impressions) * 1000, 2) )
max_cpm <- max(data$CPM)
campaign_id_for_max_cpm <- data[data$CPM == max_cpm, "campaign_id"]
campaign_id_for_max_cpm
```

## R Markdown
<font size="3">Q.3 Assume each conversion ('Total_Conversion') is worth $5, each approved conversion ('Approved_Conversion') is worth $50. ROAS
(return on advertising spent) is revenue as a percentage of the advertising spent . Calculate ROAS and round it to two decimals.
Make a boxplot of the ROAS grouped by gender for interest_id = 15, 21, 101 in one graph. Also try to use the function '+ scale_y_log10()'
in ggplot to make the visualization look better (to do so, you just need to add '+ scale_y_log10()' after your ggplot function). The x-axis
label should be 'Interest ID' while the y-axis label should be ROAS</font/>
```{r Q3}
data <- data %>% mutate(ROAS = round(((5*Total_Conversion)+ (50*Approved_Conversion))/ Spent, 2) )
data1 <- data %>%
  filter(ROAS!=Inf, interest %in% c('15','21','101'))%>%
  select(interest,gender,ROAS)#%>%
data1
ggplot(data = data1, aes(x=as.factor(interest), y=ROAS)) +geom_boxplot(aes(fill=as.factor(gender)))+ scale_y_log10()+ xlab("Interest") + ylab("ROAS")+guides(fill=guide_legend(title="Gender"))
data2 <- data1 %>%
  filter(interest=='15', gender=='0')
boxplot(data2$ROAS)
data2
p <- ggplot(data = data1, aes(x=as.factor(interest), y=as.factor(ROAS))) + geom_boxplot(aes(fill=gender)) 
p <- p + geom_jitter()
p <- p + facet_wrap( ~ interest, scales="free")
p <- p + xlab("x-axis") + ylab("y-axis") + ggtitle("Title")
p <- p + guides(fill=guide_legend(title="Legend_Title"))
p 
```

## R Markdown
<font size="3">
Q.4 Summarize the median and mean of ROAS by genders when campign_id == 1178.</font/>
```{r Q4}
data %>%
  filter(ROAS!=Inf, campaign_id==1178)%>%
  group_by(gender) %>%
  summarize(mean_size = mean(ROAS),median_size = median(ROAS))
```

## R Markdown
<font size="3">
Load the advertising1 (https://www.dropbox.com/s/inyf1fgc6dkmuxb/advertising1.csv) dataset using readr.
Convert the Clicked.on.Ad's datatype to factor through as.factor()</font/>
```{r Q5}

library(readr)
library(tidyverse)
if (!require(correlationfunnel)) install.packages("correlationfunnel")
library(correlationfunnel)
library(DataExplorer)
if (!require(WVPlots)) install.packages("WVPlots")
library(WVPlots)
library(ROCR)
if (!require(caret)) install.packages("caret")
library(caret)
if (!require(corrplot)) install.packages("corrplot")
library(corrplot)
ad<- read.csv("advertising1.csv", stringsAsFactors = FALSE)
ad$Clicked.on.Ad<-as.factor(ad$Clicked.on.Ad)
glimpse(ad)
```

## R Markdown
<font size="3">
a) We aim to explore the dataset so that we can better choose a model to implement. Plot histograms for at least 2 of the continuous
variables in the dataset. Note it is acceptable to plot more than 2. [1 point]</font/>
```{r Q5a}
ad2 <- ad %>%
  select( Area.Income,Daily.Internet.Usage,Daily.Time.Spent.on.Site)#%>%
plot_histogram(ad2)
```

## R Markdown
<font size="3">
b) Again on the track of exploring the dataset, plot at least 2 bar charts reflecting the counts of different values for different variables. Note
it is acceptable to plot more than 2. [1 point]</font/>
```{r 5b}
plot_bar(ad)
```

## R Markdown
<font size="3">
c) Plot boxplots for Age, Area.Income, Daily.Internet.Usage and Daily.Time.Spent.on.Site separated by the variable Clicked.on.Ad. To
clarify, we want to create 4 plots, each of which has 2 boxplots: 1 for people who clicked on the ad, one for those who didn't. [2 points]</font/>
```{r 5c}
ad1 <- ad %>%
  select(Age, Area.Income,Daily.Internet.Usage,Daily.Time.Spent.on.Site,Clicked.on.Ad)#%>%
plot_boxplot(ad1, by = "Clicked.on.Ad")
```

## R Markdown
<font size="3">
d) Based on our preliminary boxplots, would you expect an older person to be more likely to click on the ad than someone younger? [2
points]
Answer 5d: Based on first box plot of age vs. clicked.on.Ad where clicked.on.Ad=0 corresponds to not clicking the ad and clicked.on.Ad=1 corresponds to clicking the ad, It is clearly evident  that older people (with higher age value) are more likely to click the ad than someone younger.
Q.6
Part (a) [3 points]
1. Make a scatter plot for Area.Income against Age. Separate the datapoints by different shapes based on if the datapoint has clicked on
the ad or not</font/>
```{r 6a_part1}
library(ggplot2)
ggplot(ad, aes(Age, Area.Income))+ geom_point(aes(colour = Clicked.on.Ad))
```

## R Markdown
<font size="3">
Q6 Parta Part 2. Based on this plot, would you expect a 31-year-old person with an Area income of $62,000 to click on the ad or not?
Solution 6 Part a Part 2: The above scatter plot shows a click on Ad as a blue point and no click on ad as a red point. Note - COlor is used in place of size for readability. Based on above scatterplot, it is clear 31 year old person  with Area income of $62,000 will not click on the ad as the points around this data point are red.
Q 6 Part (b) [3 points]
1. Similar to part a), create a scatter plot for Daily.Time.Spent.on.Site against Age. Separate the datapoints by different shapes based on if
the datapoint has clicked on the ad or not</font/>
```{r 6b_part1}
library(ggplot2)
ad3<- ad %>%
  select(Age, Daily.Time.Spent.on.Site,Clicked.on.Ad)#%>%
ggplot(ad, aes(Age, Daily.Time.Spent.on.Site))+ geom_point(aes(shape = Clicked.on.Ad))
```

## R Markdown
<font size="3">
Q6 Partb Part 2. Bassed on this plot, would you expect a 50-year-old person who spends 60 minutes daily on the site to click on the ad or not?
Solution 6 Partb Part 2: The above scatter plot shows a click on Ad as a triangle and no click on ad as a circle. Based on above scatterplot, it can be clear a 50 year old person will click on the ad as most of data points up to 60 minutes time spent are traingles. 
Q7 Part a Part2
2. Generate a correlation funnel (using the correlation funnel package) to see which of the variable in the dataset have the most
correlation with having clicked the advert.
</font> 
```{r Q7_Part2}
ad4=ad
ad4$Age =as.factor(ad4$Age)
ad4$Male=as.factor(ad4$Male)
ad_binarized_tbl <- ad4 %>%
  binarize()
ad_binarized_corr_tbl <- ad_binarized_tbl %>%
  correlate(Clicked.on.Ad__1)
ad_binarized_corr_tbl
ad_binarized_corr_tbl %>%
  plot_correlation_funnel()
```

## R Markdown
<font size="3">Ques 7 Part (b) [2 points]
1. Based on the generated correlation funnel, choose the 4 most covarying variables (with having clicked the advert) and run a logistic
regression model for Clicked.on.Ad using these 4 variables. Output the summary of this model.
</font> 
```{r Q7_Partb}
ad_lr <- glm(data=ad,Clicked.on.Ad ~ Daily.Time.Spent.on.Site+Age+Area.Income+Daily.Internet.Usage, family = 'binomial')
summary(ad_lr)
```

## R Markdown
<font size="3">Q.8 [4 points]
Use type ="response" to ensure we get the predicted probabilities of clicking the advert
Append the predicted probabilities to a new column in the original dataset or simply to a new data frame. The choice is up to you,
but ensure you know how to reference this column of probabilities.
Using a threshold of 80% (0.8), create a new column in the original dataset that represents if the model predicts a click or not for that
person. Note this means probabilities above 80% should be treated as a click prediction.
Now using the caret package, create a confusion matrix for the model predictions and actual clicks. Note you do not need to graph or
plot this confusion matrix.
How many false-negative occurrences do you observe? Recall false negative means the instances where the model predicts the case
o be false when in reality it is true. For this example, this refers to cases where the ad is clicked but the model predicts that it isn't
</font> 
```{r Q8}
ad$predictpr =predict(ad_lr, ad, type="response")
ad$predictval <- ifelse(ad$predictpr>0.8, 1,0)
xtab <- table(ad$Clicked.on.Ad,ad$predictval)
confusionMatrix(xtab)
```

## R Markdown
<font size="3">Q.8 [4 points]
Based on above confusion matrix number of false negatives when model predicts false when actually it is true are 36
</font> 
